Supplementary information for ``CLM5-PPE"

### 2024-10-08 ms/supp.tex
overleaf

@@

\begin{figure}[h]
\centering
\includegraphics[width=30pc]{../figs/supp/AF2095_rankings.png}
\caption{Comparing parameter rankings with and without the errant gridcells from Supp Figure S4 across a selection of output variables.}
\label{supp:abug}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/supp/funbug.png}
\caption{Parameter rankings for nitrogen uptake parameters subject to a recently uncovered CLM bug. The values for \textit{kn\_nonmyc} and \textit{kc\_nonmyc} had been accidentally transposed.}
\label{supp:funbug}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=30pc]{../figs/supp/AF2095_rankings.png}
\caption{Comparing parameter rankings with and without the errant gridcells from Supp Figure S6 across a selection of output variables.}
\label{supp:abug}
\end{figure}
